Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-12 paper/ms.tex
update catalogscatter plot

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{f6.pdf}
		\vspace{-0.2cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the dark blue circles; \nmaybes\ candidate CQVs are light blue circles.
      The top panels show the \nstarssearched\ target stars with 120-second cadence data
      as the shaded gray background;
      darker regions correspond to a larger relative number of searched stars.
      The lower-left panel compares the rotation--color distribution of the CQVs, and candidate CQVs, against the rotation
      periods of K- and M-dwarfs in the Pleiades from \citet{2016AJ....152..114R}.
      Note the scale change for the period $P$ from days to hours in the middle panel of the lower row.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{f6.pdf}
		\vspace{-0.1cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the dark blue circles; \nmaybes\ candidate CQVs are light blue circles.
      The top panels show the \nstarssearched\ target stars with 120-second cadence TESS data
      as the shaded gray background;
      darker regions correspond to a larger relative number of searched stars.
      The lower-left panel compares the rotation--color distribution of CQVs against the rotation
      periods of K- and M-dwarfs in the Pleiades from \citet{2016AJ....152..114R}.
      The lower-middle panel plots the derived corotation radii
      $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in units of stellar radii against the measured
      CQV periods, in units of hours.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}
